Quality Definitions of Qualities

### 2019-10-05 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated Performance, Maintainability, Reusability

Performance considerations can make certification challenging, since QA becomes
more difficult for more complex code.  However, as
Roache~\cite[p.~355]{Roache1998} points out, using simpler algorithms and
reducing the number of options in general purpose code, is not always a
practical option.

@@

Maintainability is necessary in scientific software, since change, through
iteration, experimentation and exploration, is inevitable.  Models of physical
phenomena and numerical techniques necessarily evolve over
time~\cite{CarverEtAl2007, SegalAndMorris2008}.  Proper documentation, designed
with change in mind, can greatly assist with change management.  QA activities
need to take the need for creativity into account, while not smothering
it~\cite[p.~352]{Roache1998}.

@@

Reusability provides support for the quality of reliability, since reliability
is improved by reusing trusted components~\cite{Dubois2005}.  (Care must still
be taken with reusing trusted components, since blind reuse in a new context can
lead to errors, as dramatically shown in the Ariane 5
disaster~\cite[p.~37--38]{OliveiraAndStewart2006}.)  The odds of reuse are
improved when it is considered right from the start.

>>>>

The degree to which a system or component accomplishes its designated functions within given constraints, such as speed, accuracy, or memory usage \cite{IEEEStdGlossarySET1990}.
Performance considerations can make certification challenging, since QA becomes more difficult for more complex code.  However, as Roache~\cite[p.~355]{Roache1998} points out, using simpler algorithms and reducing the number of options in general purpose code, is not always a practical option.

@@

The ease with which a software system or component can be modified to correct faults, improve performance or other attributes, or adapt to a changed environment \cite{IEEEStdGlossarySET1990}. ISO/IEC 25010 refers to maintainability as the degree of effectiveness and efficiency with which a product or system can be modified by the intended maintainers \cite{ISO/IEC25010}.
Maintainability is necessary in scientific software, since change, through iteration, experimentation and exploration, is inevitable.  Models of physical phenomena and numerical techniques necessarily evolve over time~\cite{CarverEtAl2007, SegalAndMorris2008}.  Proper documentation, designed with change in mind, can greatly assist with change management.  QA activities need to take the need for creativity into account, while not smothering
it~\cite[p.~352]{Roache1998}.

@@

The degree to which a software module or other work product can be used in more than one software system \cite{IEEEStdGlossarySET1990}. Reusability provides support for the quality of reliability, since reliability
is improved by reusing trusted components~\cite{Dubois2005}.  (Care must still
be taken with reusing trusted components, since blind reuse in a new context can lead to errors, as dramatically shown in the Ariane 5 disaster~\cite[p.~37--38]{OliveiraAndStewart2006}.)  The odds of reuse are improved when it is considered right from the start.
